%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

%------------------------------------------------

\name{Henry Oberholtzer} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{\href{tel:5304004674}{(530)-400-4674} \\ \href{mailto:henryoberholtzer@gmail.com}{henryoberholtzer@gmail.com} \\ \href{https://www.henryoberholtzer.com}{henryoberholtzer.com}} % Contact information
% \address{\href{https://github.com/henry-oberholtzer}{github.com/henry-oberholtzer} \\ \href{https://www.linkedin.com/in/henryoberholtzer}{linkedin.com/in/henryoberholtzer}}

\begin{document}

\begin{flushleft}
	Full-stack web developer with roots in music and project management, passionate about collaboration, open source code, and techno. \hfill
\end{flushleft}

\begin{rSection}{Projects}
	\begin{rSubsection}{Record Store}{2023}{Inventory Manager}{\href{https://github.com/henry-oberholtzer/record-store}{github.com/henry-oberholtzer/record-store}}
		\item A React web application written in TypeScript, using Redux \& Vite, with a custom repsponsive UI.
		\item Follows functional programming practices, currying, and has a temporary database.
		\item Allows user access to full CRUD functionality, with changes saved locally.
	\end{rSubsection}
	\begin{rSubsection}{Currency Exchange}{2023}{API-based web app}{\href{https://github.com/henry-oberholtzer/solar-system-age}{github.com/henry-oberholtzer/solar-system-age}}
		\item Written in JavaScript and built with Webpack, returns live exchange rates for 161 currencies.
		\item Minimizes necessary API calls by using local storage to save rates.
	\end{rSubsection}
\end{rSection}

\begin{rSection}{Education}

	\begin{rSubsection}{Full-Stack Web Development Certification}{June 2024}{Epicodus}{Portland, OR}
		\item TypeScript, React.js, C\#/.NET, NoSQL, MySQL, HTML, CSS
		\item Full-time class structure simulating an agile development environment with daily pair programming.
		\item Gained a foundation of best practices the skill to adopt new languages and technologies with ease.
		\item Created a wealth of independent projects to showcase both my skill and growth as a developer.
	\end{rSubsection}
	\begin{rSubsection}{Certification in Project Management}{June 2023}{PSU CEPE}{Portland, OR}
		\item Acquired skills for agile methodologies, planning, stakeholder management, and leadership strategies
	\end{rSubsection}
	\begin{rSubsection}{B.A. in Music Composition}{May 2021}{Reed College}{Portland, OR}
		\item \textbf{Senior Thesis:} Waveform Transmission: Minimalism and Dynamic Expression in Techno
		\item Focused on studying the expressive and compositional techniques in minimal techno.
		\item Wrote a historical overview covering minimalist art music and birth of techno.
		\item I wrote, produced and recorded two tracks based on the results of my musical analysis.
	\end{rSubsection}


\end{rSection}

\begin{rSection}{Experience}

	\begin{rSubsection}{Smith Teamaker}{June 2021 - September 2023}{Tasting Room Attendant}{Portland, OR}
		\item Represented the Smith Teamaker brand, fielded customer questions and concerns.
		\item Prepared and presented beverages and tasting experiences to customers in a fast paced environment.
		\item Offered in-depth knowledge of tea offerings, tea manufacturing and brand history to customers.
	\end{rSubsection}

	\begin{rSubsection}{Reed College}{Jan 2019 - October 2019}{Orientation Coordinator}{Portland, OR}
		\item Planned the new student orientation for an incoming class of over 300 students.
		\item Hired, scheduled and trained a team of 25 student workers to help run orientation.
		\item Coordinated departments on campus to carry out over 100 events through the week.
		\item Involved in all stages of event execution to assure events ran without problem.
	\end{rSubsection}

\end{rSection}

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Langauges     & JavaScript, TypeScript, JSX, C\#/.NET, HTML, CSS      \\
		Tools         & React, Vite.JS, BootStrap, NoSQL, SQL, REST           \\
		Interpersonal & Creative Leadership, Team Coordination, Communication
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
